Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-06-18 inst/doc/nonparametric-bayes.Rmd
run in small noise regime

```{r pdf-options, echo=FALSE, cache=FALSE, include=FALSE}
library(ggplot2)
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```

>>>>

```{r pdf-options, echo=FALSE, cache=FALSE, include=FALSE}
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
library(ggplot2)
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```
